Stellar Radiation is Critical for Regulating Star Formation and Driving Outflows in Low Mass Dwarf Galaxies

### 2019-03-19 thesis/chapters/ch_introduction.tex
reformatting code cases

A full, detailed model of radiative cooling, heating, non-equillibrium chemistry, and dust is generally far too computationally expensive to include in galaxy-scale simulations. For this reason, many large-scale cosmological simulations assume that all gas is optically thin and that all molecules and ionization states exist in equilibrium. This allows for the quick use of tabulated look-up tables for radiative cooling and heating, often produced using \code{CLOUDY} \citep{Cloudy2013}, that depend on gas density, temperature, metallicity, and redshift (which sets the UVB heating rate). More complex simulations often track some number (usually $< 10$) of species involved in primordial chemistry in order to better account for non-equilibrium effects and \Hmolecular production, though with noted increases in memory requirements and computational cost. Some of the most advance models to-date can account for well over 10$^2$ individual chemical reactions involving $>$ 20 elements and molecules \citep[e.g.][]{Richings2015,Richings2018}; but these are typically prohibitively expensive to run on large scales. In this \dissertation we adopt the chemistry and radiative cooling and heating physics models available in the newly developed, open-source library \code{GRACKLE} \citep{GrackleMethod}. The exact physics included in our simulations are discussed in greater detail in Chapter~\ref{ch:chapter1}, but we note that improvements to \code{GRACKLE} have been made as the direct result of the research conducted during this \dissertation.
%mention that I made improvements to this?

>>>>

A full, detailed model of radiative cooling, heating, non-equillibrium chemistry, and dust is generally far too computationally expensive to include in galaxy-scale simulations. For this reason, many large-scale cosmological simulations assume that all gas is optically thin and that all molecules and ionization states exist in equilibrium. This allows for the quick use of tabulated look-up tables for radiative cooling and heating, often produced using \code{cloudy} \citep{Cloudy2013}, that depend on gas density, temperature, metallicity, and redshift (which sets the UVB heating rate). More complex simulations often track some number (usually $< 10$) of species involved in primordial chemistry in order to better account for non-equilibrium effects and \Hmolecular production, though with noted increases in memory requirements and computational cost. Some of the most advance models to-date can account for well over 10$^2$ individual chemical reactions involving $>$ 20 elements and molecules \citep[e.g.][]{Richings2015,Richings2018}; but these are typically prohibitively expensive to run on large scales. In this \dissertation we adopt the chemistry and radiative cooling and heating physics models available in the newly developed, open-source library \code{GRACKLE} \citep{GrackleMethod}. The exact physics included in our simulations are discussed in greater detail in Chapter~\ref{ch:chapter1}, but we note that improvements to \code{GRACKLE} have been made as the direct result of the research conducted during this \dissertation.
%mention that I made improvements to this?
